Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-09 hotstorage13/intro.tex
ad

Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were build a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio. 
%at the expense of processing latency.  
At the same time, we ensure the aggregate read/write throughput of the system 
is sufficiently scalable  for dealing with backup of a large number of virtual machine images. 
% This business model partially  resembles that of Amazon Glacier.

%Our solution  only uses a very small amount of memory space during backup while completing  snapshot backup and 
%deletion in a reasonable amount of time. 
The traditional approach to  deduplication for backup is an inline approach which follows
a sequence of VM block reading, duplicate detection,  and non-duplicate  block write to the 
backup storage.  
Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
among all machines before performing actual data backup. Each machine
accumulates detection requests and  then performs pre-detection   partition by partition 
with minimal resource usage.
Fingerprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
reference counting management.  
% as the entire process can also be divided into a
%parition-wise  deletion. 
With careful parallelism management and message buffering during cross-machine data exchange,
this pre-detection scheme can provide  a sufficient throughput for backup.

>>>>

Among the three factors - time, cost and de-deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were build a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and do fast comparison.  This leads to a compromise on cost. 
The objective of our project is to lower the cost incurred while sustaining the highest de-duplication ratio
and  the sufficient deduplication  throughput for dealing with a large number of virtual machine images. 
% This business model partially  resembles that of Amazon Glacier.

%Our solution  only uses a very small amount of memory space during backup while completing  snapshot backup and 
%deletion in a reasonable amount of time. 
The traditional approach to  deduplication for backup is an inline approach which follows
a sequence of VM block reading, duplicate detection,  and non-duplicate  block write to the 
backup storage.  
Our key idea  is to  first perform parallel duplicate pre-detection for VM content blocks 
among all machines before performing actual data backup. Each machine
accumulates detection requests and  then performs pre-detection   partition by partition 
with minimal resource usage.
Fingerprint based partitioning allows highly parallel duplicate pre-detection  and also simplifies 
reference counting management.  
% as the entire process can also be divided into a
%parition-wise  deletion. 
With careful parallelism and buffer  management,
this pre-detection scheme can provide  a sufficient throughput for backup.
